The Diminishing Returns of Music in the Digital Era

### 2024-04-14 paper/paper.qmd
data section nearly done

print(average_revenue_table)
```

>>>>

print(average_revenue_table)
```
\newpage

```{r}
#| echo: false
#| eval: true
#| label: tbl-revenuechange
#| warning: false
#| results: asis
#| 
music_data <- read_csv("/Users/victortimir/music-industry-analysis/data/raw_data/musicdata-1.csv")

top_formats <- music_data %>%
  group_by(format) %>%
  summarise(total_revenue = sum(value_actual, na.rm = TRUE)) %>%
  top_n(5, total_revenue) %>%
  pull(format)

top_formats_data <- music_data %>%
  filter(format %in% top_formats)

top_formats_data <- top_formats_data %>%
  group_by(format) %>%
  mutate(yoy_change = (value_actual / lag(value_actual) - 1) * 100) %>%
  ungroup()

ggplot(top_formats_data, aes(x = year, y = yoy_change, color = format)) +
  geom_line() +
  scale_y_continuous(limits = c(-100, 100),
                     labels = scales::percent) +
  labs(title = "Year-Over-Year Revenue Change for Top Music Formats",
       x = "Year",
       y = "Percentage Change",
       color = "Format") +
  theme_minimal() +
  theme(legend.position = "bottom")
```
